Surface programmable materials

### 2024-09-04 paper/main.tex
Updates from Overleaf

Energy based models are probability one of the most powerful models for computation.
The Ising model is not only capable of universal computation~\cite{gu2012encoding}, and it can be used to formulate many NP problems~\cite{lucas2014ising,mohseni2022ising}.
However, they are notoriously hard to thermalize, even with the help of quantum entanglement~\cite{boixo2013experimental, boixo2014evidence}.

Intrigued by the question that how to lower the energy of an Ising machine, we propose a new type of TC, which is based on a translational invariant crystalline structure.
We first show that the crystalline structure can be programmed on its surfaces to perform universal computation.
Then we show that if we thermalize the crystal from the ``deterministic direction'', the crystal can thermalize in time almost linear to the size of the crystal, i.e. efficient computation can be performed.

>>>>

Energy based models are probability one of the most powerful models for computation.
The Ising model is not only capable of universal computation~\cite{gu2012encoding}, and it can be used to formulate many NP problems~\cite{lucas2014ising,mohseni2022ising}.
However, they are notoriously hard to thermalize, even with the help of quantum entanglement~\cite{boixo2013experimental, boixo2014evidence}.
There is no evidence yet that they can significantly outperform existing algorithms run on classical computers~\cite{}.
Even when the encoded problem is an easy one, it is not guaranteed that the system can thermalize in polynomial time as we will show in the main text.

Intrigued by the question that how to efficiently thermalize an Ising machine and drive it to the ground state, we propose a new type of TC, which is based on a translational invariant crystalline structure.
We first show that the crystalline structure can be programmed on its surfaces to perform universal computation.
Then we show that if we thermalize the crystal from the ``deterministic direction'', the crystal can thermalize in time almost linear to the size of the crystal, i.e. efficient computation can be performed.
